---
title: 'Laboratory Exercise Week 2'
author: "Your Name and Section"
date: "Todays Date"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Directions*: 

* Write your R code inside the code chunks after each question.
* Write your answer comments after the `#` sign.
* To generate the word document output, click the button `Knit` and wait for the word document to appear.
* RStudio will prompt you (only once) to install the `knitr` package.
* Submit your completed laboratory exercise using Blackboard's Turnitin feature. Your Turnitin upload link is found on your Blackboard Course shell under the Laboratory folder.

***

1. 1. The `RailTrail` dataset within the `mosaic` package includes the counts of crossings of a rail trail in Northampton, Massachusetts for 90 days in 2005. City officials are interested in understanding usage of the trail network, and how it changes as a function of temperature and day of the week.
      i) Check the structure of the`RailTrail`. 
      ii) How many variables and observations are in the data set? 
      iii) Which variables are `integer` type?
      iv) Display the first 4 rows of the data.

## Code chunk
```{r} 
# Insert your code for this question after this line
trial.vec <- 1:20
trial.vec

# last R code line
```


2. 

```{r}
# Insert your code for this question after this line


```
  
3. 

```{r}
# Insert your code for this question after this line


```

4. 

```{r}
# Insert your code for this question after this line


```