---
title: "Week 1: R Software Introduction"
author: "written by Junvie Pailden"
output: 
  github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "figures/",
  fig.height = 3,
  fig.width = 4,
  fig.align = "center"
)
```

## The R Software

R is a programming environment for data analysis, graphics and statistical computing. The R language is widely used among statisticians for developing statistical software and data analysis.

R processes commands entered by the user, who types the commands at the console, or submits the commands from a file called a script.

When the user use the console, each command or expression
to be evaluated is typed at the command prompt, and immediately evaluated
when the `Enter` key is pressed.

When the user submits the commands from a file, each line of code is evaluated by hitting `Cntrl + R` or `Cntrl + Enter` for PC or hitting `Cmd + R` or `Cmd + Enter` for Mac.

Helpful tips

* Press the up-arrow key to recall commands and edit them.
* Use the `Esc (Escape)` key to cancel a command.
* Write comments after `#` sign.

## What is RStudio?

RStudio (<http://www.rstudio.org>) is R's popular front-end or integrated development environment (IDE). We will use RStudio for all class related computation and analysis. RStudio provides syntax highlighting, code completion and smart indentation. Some of RStudios features includes

* plot history, zooming, and flexible image and PDF export;
* integrated R help and documentation;
* generating word or pdf file output;
* searchable command history.

## Using R as a simple calculator

Start the RStudio system, the cursor is waiting for you to type in some R commands. For example, use R as a simple calculator:

```{r 01-w01}
7 + 4  # addition

8 * 9 # multiplication

17 / 3 # division

4 ^ 3 # power

(1 + 0.03)^5 # association

exp(4) # exponential function

log(12) # natural log function

3.1415 * log(3)/(7 - atan(8))
```

## Assignment Operator

Results of calculations can be stored in objects using the assignment operators:

* an arrow (`<-`) formed by a smaller than character and a hyphen without a space;
* the equal character (`=`).

Many R users have suggested using `<-`, not `=`, for assignment.

```{r 02-wk01}
x <- sin(0)
y <- 3.1415 * cos(pi)
z <- x + y
x
y
z
```

## Storing Data in R

*Example 1. (Temperature Data).* Average annual temperatures in New Haven,
CT, were recorded in degrees Fahrenheit, as

| Year             | 1968 | 1969 | 1970 | 1971 |
|------------------|------|------|------|------|
| Mean temperature | 51.9 | 51.8 | 51.9 | 53   |

The combine function `c()` creates a vector from its arguments, and the result can be stored
in user-defined vectors. We use the combine function to enter our data and
store it in an object named `temps`.


```{r 03-wk01}
temps <- c(51.9, 51.8, 51.9, 53)
temps
```

Suppose that we want to convert the Fahrenheit temperatures (F) to Celsius
temperatures (C). The formula for the conversion is $C = 5/9
(F −32)$.

```{r 04-wk01}
(5/9) * (temps - 32)
```

Let's create another vector containing the year the temperatures were taken.


```{r 05-wk01}
years <- c(1968, 1969, 1970, 1971)
years
```

The preferred form for variable names is all lower case letters and words separated with dots `(variable.name)`.

We can use the function `cbind` to combine the two vectors (`years` and `temps`) into a matrix.


```{r 06-wk01}
temp.data <- cbind(years, temps)
temp.data
```

## Objects in R

Vectors and matrices are two of several types of objects in R. Other types of objects are lists, factors, and data frames. More on this later.

A vector can be defined according to the data type it contains. There are

* numeric vectors;
* logical (or Boolean) vectors;
* character (or string) vectors.

```{r 07-wk01}
num <- c(3, 3.1, 3.14, pi, -pi, cos(pi))
num
char <- c("I", "Love", "Pie")
char
char[2] # second entry of vector char
char[-3] # displays the sub-vector excluding the 3 entry
```

If a vector mixes different data types, R will store it as a character vector.

```{r 08-wk01}
mixed <- c("I", "Love", 3)
mixed
```

Logical vectors are often defined as the result of control actions on numerical or character vectors.

```{r 09-wk01}
num
logic1 <- num > 2
logic1
```

Vectors can be created using sequences using the operator `:` or using `seq()` function.

```{r 10-wk01}
v.for <- 1:15 # generate integer sequence from 1 to 15
v.for
v.back <- 15:1  # generate integer sequence from 15 to 1
v.back
seq.by <- seq(from = 1, to = 15, by = 2) # generate a sequence from 1 to 15 incremented by 2
seq.by
seq.len <- seq(from = 1, to = 15, length.out = 8) # generate a sequence from 1 to 15 of length 8
seq.len
seq.len[1:5] # displays the first 5 entries
```

## The R Help System
The help search functions are also available using the functions `help` and `help.search`, and the corresponding shortcuts `?` and `??`.

* `help("keyword")` or `?keyword` displays help for `“keyword”`.
* `help.search("keyword")` or `??keyword` searches for all objects containing `“keyword”`.

For example, when looking for information on computing the average or mean of a vector

```{r 11-wk01}
help("mean") # or
?mean        # scroll to the bottom to see examples
x <- c(0:10, 50)
x
mean(x)
```



***


# Laboratory Exercise for Week 1 (10 points)

*Directions*: 

* Download this week's exercise file and open the file using RStudio. Right click the link and "Save as..." to your desktop. (<https://goo.gl/noVy6g>)
* This file type is called RMarkdown and is used widely to share and collaborate R outputs. More information is found on this link (<http://rmarkdown.rstudio.com/articles_docx.html>). 
* All R codes should be written inside code chunks. Check (<http://rmarkdown.rstudio.com/authoring_rcodechunks.html>).
* Submit your completed laboratory exercise using Blackboard's Turnitin feature. Your Turnitin upload link is found on your Blackboard Course shell under the Laboratory folder.

1. Create a vector of three elements `(2,4,6)` and name that vector `vec.a`. Create a second vector, `vec.b`, that contains `(8,10,12)`. 
    a. Add these two vectors together and name the result `vec.c`.
    b. Create a vector, named `vec.d`, that contains only two elements `(14,20)`. Add this vector to `vec.a`. What is the result and what do you think `R` did (look up the recycling rule using `Google`)? What is the warning message that `R` gives you?
    c. Next add 5 to the vector `vec.a`. What is the result and what did `R` do? Why doesn’t it give you a warning message similar to what you saw in the previous problem?

2. Generate the vector of even numbers `{2, 4, 6, . . . , 20}`
    a. Using the `seq()` function and
    b. Using the `a:b` shortcut and some subsequent algebra. *Hint: Generate the vector 1-10 and then multiple it by 2.*
  
3. Create a vector `y` containing `(2, 2, 2, 2, 4, 4, 4, 4, 8, 8, 8, 8)` using the `rep()` function. You might need to check the help file for `rep()` by typing `?rep` in the console to see all of the options that `rep()` will accept. In particular, look at the optional argument `each=`.
    a. Find the mean of vector `y` using the function `mean()`.
    b. Use google search to find the function in `R` that computes the variance of a vector and find the variance of `y`. 

4. The vector `letters` is a built-in vector to `R` and contains the lower case English alphabet.
    a. Extract the 9th element of the `letters` vector.
    b. Extract the sub-vector that contains the 9th, 11th, and 19th elements.
    c. Extract the sub-vector that contains everything except the last two elements.
