---
title: 'Laboratory Exercise Week 2'
author: "Your Name and Section"
date: "Todays Date"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Directions*: 

* Write your R code inside the code chunks after each question.
* Write your answer comments after the `#` sign.
* To generate the word document output, click the button `Knit` and wait for the word document to appear.
* RStudio will prompt you (only once) to install the `knitr` package.
* Submit your completed laboratory exercise using Blackboard's Turnitin feature. Your Turnitin upload link is found on your Blackboard Course shell under the Laboratory folder.

***

1. You will work with a matrix whose entries are all prime numbers below 30.
      i)  Create this matrix using the function `matrix()` with five rows. Save the matrix as `P`.
      ii) Extract the second and third row out of `P`.
      iii) Extract the entry in the fourth row and first column of `P`.
      iv) Generate the transpose of the matrix using the function `t()`. What is the new dimension of this matrix.

### Code chunk
```{r}
# Insert your code for this question after this line


```

2. Create and manipulate a data frame.
      i) Create a `data.frame` named `my.trees` that has the following columns:
          - `Girth = c(8.3, 8.6, 8.8, 10.5, 10.7, 10.8, 11.0)`
          - `Height = c(70, 65, 63, 72, 81, 83, 66)`
          - `Volume = c(10.3, 10.3, 10.2, 16.4, 18.8, 19.7, 15.6)`
      ii) Extract the fifth observational unit.
      iii) Extract the `Girth` column referring to it by name.
      iv) Print out a data frame of all the observations except for the last observation.


### Code chunk
```{r}
# Insert your code for this question after this line


```

3. The popular `iris` data set gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica. The `iris` data set is included with every R installation.    
      i) Check the structure of the`iris` data.   
      ii) How many variables and observations are in the data set?  
      iii) Which variables are `numeric` type?  
      iv) Display the first 4 rows of the data.  

### Code chunk
```{r} 
# Insert your code for this question after this line


# last R code line
```



  
4.  You will work with the passenger Titanic data found on this [link](<https://goo.gl/NHb1Pg>). 
      i) Read this data directly from the web using its URL.
      ii) Read this data by saving it first into your working directory. Check your working directory using `getwd()` or change its location using the steps covered in the lesson.
      iii) How many passengers and what variables are in the data set? 
      iv) Display the first 5 rows of the data.

### Code chunk
```{r}
# Insert your code for this question after this line


```

